Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
changed mus to phis

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
\Updownarrow \notag\\
\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
\end{gather}
The second equivalence was also earlier observed by Shulman \cite{Shulman2008}. In more detail, if $(\mu,\mu_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\mu_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\mathbf{1}\xrightarrow{\mu_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map. 
\end{proof}

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\mu,\mu_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\mu_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}

@@

By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits. Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
\begin{displaymath}
 F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
\end{displaymath}
describes the construction of the adjunction from the original $F$. Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\mu_0(*)$ according to \cref{eq:initialinfibre} for $(\mu,\mu_0)$ the monoidal structure of $F$.

@@

A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence. A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds. A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\mu_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\mu_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality. This is commonly also called `weak monoidal' pseudofunctor. A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \mu_{a,b}\cong\mu_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one. RIGHT???

>>>>

\begin{proof}
This was shown by Moeller and the third author \cite[Theorems~3.13\&4.1]{MV}. In summary, for a cocartesian base we have correspondences
\begin{gather}
\textrm{lax monoidal pseudofunctors }F\maps(\A,+)\to(\Cat,\times) \notag\\
\Updownarrow \notag\\
\textrm{monoidal opfibrations }U\maps(\X,\otimes)\to(\A,+) \label{monGroth}\\
\Updownarrow \notag\\
\textrm{pseudofunctors }F\maps\A\to\bicat{MonCat} \notag
\end{gather}
The second equivalence was also earlier observed by Shulman \cite{Shulman2008}. In more detail, if $(\phi,\phi_0)$ is the lax monoidal structure of the pseudofunctor $F$ as recalled in \cref{sec:2cats}, each fibre category $\X_a=F(a)$ obtains a monoidal structure via
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\mathbf{1}\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map. 
\end{proof}

@@

Finally, if the original pseudofunctor is in fact lax monoidal $(F,\phi,\phi_0)$, the monoidal Grothendieck construction of \cref{lem:MonGroth} in the cocartesian case expresses $\bot_a$ as follows by \cref{eq:explicitstructure1}:
\begin{equation}\label{eq:initialinfibre}
\mathbf{1}\xrightarrow{\phi_0}F(0_\A)\xrightarrow{F(u_a)}F(a) 
\end{equation}
\end{rmk}

@@

By \cref{cor:fcocMonGroth}, when $F$ as an ordinary pseudofunctor factors through $\Rex$, the Gro\-the\-ndieck construction gives rise to a finitely cocomplete $\inta F$ such that the corresponding opfibration $U\maps\inta{F}\to\A$ preserves all finite colimits. Moreover, by \cref{prop:opfibtolari}, $U$ has a left adjoint $L\maps\A\to\inta F$ with $UL=1_\A$. Diagrammatically,
\begin{displaymath}
 F\maps\A\to\Cat\quad\mapsto\quad\begin{tikzcd}[baseline=.3]\inta F\ar[d,"U"'] \\ \A \end{tikzcd}\quad\mapsto\quad\begin{tikzcd}\A\ar[r,bend left,pos=.55,"L"]\ar[r,phantom,"\bot"description] & \inta F\ar[l,bend left,pos=.45,"U"]\end{tikzcd}
\end{displaymath}
describes the construction of the adjunction from the original $F$. Explicitly, the left adjoint picks the initial object in the finitely cocomplete fibre $L(a)=(a,\bot_a)$, also expressed as $F(u_a)\circ\phi_0(*)$ according to \cref{eq:initialinfibre} for $(\phi,\phi_0)$ the monoidal structure of $F$.

@@

A \define{monoidal} bicategory $\bicat{A}$ comes with a pseudofunctor $\otimes\maps\bicat{A}\times\bicat{A}\to\bicat{A}$ and a unit object $I$ that are associative and unital up to coherent equivalence. A \define{braided} monoidal bicategory comes with a pseudonatural equivalence $\beta_{a,b}\maps a\ot b\to b\ot a$ and appropriate invertible modifications; it is \define{sylleptic} if there is an appropriate invertible modification $1_{a\ot b}\Rrightarrow\beta_{b,a}\circ\beta_{a,b}$ and it is \define{symmetric} if one further axiom holds. A \define{lax monoidal} pseudofunctor between monoidal bicategories $F\maps\bicat{A}\to\bicat{B}$ is a pseudofunctor equipped with pseudonatural transformations with components $\phi_{a,b}\maps Fa\otimes Fb\to F(a\otimes b)$ and $\phi_0\maps I\to FI$ along with coherent invertible modifications for associativity and unitality. This is commonly also called `weak monoidal' pseudofunctor. A \define{braided lax monoidal} pseudofunctor between braided monoidal bicategories comes with an appropriate invertible modification with components $F(\beta_{a,b})\circ \phi_{a,b}\cong\phi_{b,a}\circ \beta_{Fa,Fb}$; a \define{sylleptic lax monoidal} pseudofunctor satisfies one extra condition and a \define{symmetric lax monoidal} pseudofunctor between symmetric monoidal bicategories is just a sylleptic one. RIGHT???
